\texttt{\Large{pyannote.metrics}}: a toolkit for reproducible evaluation,\\ diagnostic, and error analysis of speaker diarization systems

### 2017-05-22 paper.tex
fix: fix typos found by reviewers

A typical speaker diarization pipeline is depicted in Figure~\ref{fig:pipeline}.
The first step is usually dedicated to speech activity detection, where the objective is to get rid of all non-speech regions.
Then, speaker change detection aims at segmenting speech regions into homogeneous segments.
The subsequent clustering step tries to group those speech segments according to the identity of the speaker.
Finally, an optional supervised classification step may be applied to actually identity every speaker cluster in a supervised way.

@@

\begin{eqnarray*}
   \text{purity} & = & \frac{\displaystyle \sum_{\text{cluster}} \max_{\text{speaker}} |\text{cluster} \cap \text{speaker}|  }{\displaystyle \sum_{\text{cluster}} |\text{cluster}|} \\
  \text{coverage} & = & \frac{\displaystyle \sum_{\text{speaker}} \max_{\text{cluster}} |\text{speaker} \cap \text{cluster}|  }{\displaystyle \sum_{\text{speaker}} |\text{speaker}|} \\
\end{eqnarray*}
where $|\text{speaker}|$ (respectively $|\text{cluster}|$ is the speech duration of this particular reference speaker (resp. hypothesized cluster), and  $|\text{speaker} \cap \text{cluster}|$ is the duration of their intersection.
Over-segmented results (\emph{e.g.} too many speaker clusters) tend to lead to high purity and low coverage, while under-segmented results (\emph{e.g.} when two speakers are merged into one large cluster) lead to low purity and higher coverage.

>>>>

A typical speaker diarization pipeline is depicted in Figure~\ref{fig:pipeline}.
The first step is usually dedicated to speech activity detection, where the objective is to remove all non-speech regions.
Then, speaker change detection aims at segmenting speech regions into homogeneous segments.
The subsequent clustering step tries to group those speech segments according to the identity of the speaker.
Finally, an optional supervised classification step may be applied to actually identify every speaker cluster in a supervised way.

@@

\begin{eqnarray*}
   \text{purity} & = & \frac{\displaystyle \sum_{\text{cluster}} \max_{\text{speaker}} |\text{cluster} \cap \text{speaker}|  }{\displaystyle \sum_{\text{cluster}} |\text{cluster}|} \\
  \text{coverage} & = & \frac{\displaystyle \sum_{\text{speaker}} \max_{\text{cluster}} |\text{speaker} \cap \text{cluster}|  }{\displaystyle \sum_{\text{speaker}} |\text{speaker}|} \\
\end{eqnarray*}
where $|\text{speaker}|$ (respectively $|\text{cluster}|$) is the speech duration of this particular reference speaker (resp. hypothesized cluster), and  $|\text{speaker} \cap \text{cluster}|$ is the duration of their intersection.
Over-segmented results (\emph{e.g.} too many speaker clusters) tend to lead to high purity and low coverage, while under-segmented results (\emph{e.g.} when two speakers are merged into one large cluster) lead to low purity and higher coverage.
